
% Resume in Latex
% Author :Tejasv Kumar
% Based off of: https://github.com/guptatejasv/My_resume_TEJ.git

\documentclass[letterpaper,11pt]{article}


\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


\RequirePackage{tikz}
\RequirePackage{xcolor}
\RequirePackage{fontawesome}
\usepackage{tikz}
\usetikzlibrary{svg.path}




\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}






%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}


% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}




% \pagestyle{fancy}
% \fancyhf{}  % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}


% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}


\urlstyle{same}


\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}


% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]


% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1


%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
     
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}




\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}


\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}


\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}




\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%




\begin{document}


%----------HEADING----------




\begin{center}
    {\Huge \scshape Tejasv Kumar} \\ \vspace{1pt}
    Full Stack Developer  \\ \vspace{1pt}
    Hardoi,Uttar Pradesh \\ \vspace{1pt}
    \small \href{tel:+918303484340}{ \raisebox{-0.1\height}\faPhone\ \underline{+91-8303484340} ~} \href{mailto:guptatejasv86086@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{guptatejasv86086@gmail.com}} ~
    \href{https://www.linkedin.com/in/kumar-tejasv86086}{\raisebox{-0.2\height}\faLinkedinSquare\ \underline{kumar-tejasv86086}}  ~
    \href{https://github.com/guptatejasv}{\raisebox{-0.2\height}\faGithub\ \underline{guptatejasv}} ~
    \href{https://www.hackerrank.com/profile/georgejack166}{\raisebox{-0.2\height}\faHackerrank\ \underline{georgejack166}} ~
    % \href{https://codeforces.com/profile/yourid}{\raisebox{-0.2\height}\faPoll\ \underline{yourid}}
    % \vspace{-8pt}
\end{center}




%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {ShivSys Softwares Pvt. Ltd., Noida \href{certificate Link}{\raisebox{1\height}\faExternalLink }}{01 2025- Current}
      {\underline{Software Engineer Trainee}}{Noida}
      \vspace{-0pt}
      \resumeItemListStart
        \resumeItem{\normalsize{As a Software Developer at ShivSys Softwares Pvt Ltd, I played a key role in developing and enhancing the \textbf{FitExGo} mobile application using \textbf{React Native} for both Android and iOS platforms.}}
         \resumeItem{\normalsize{ \textbf{Frontend Development}: Implemented intuitive UI/UX features, ensuring seamless navigation and engaging user interactions. Integrated Context API for efficient theme switching, improving user customization.}}
          \resumeItem{\normalsize{\textbf{Serverless Solutions}: Transitioned critical backend processes to \textbf{AWS Lambda} for improved scalability, reduced latency, and optimized performance. }}
           \resumeItem{\normalsize{\textbf{AWS Integration}: Utilized AWS services like \textbf{EC2, S3} for secure data storage, content delivery, and maintaining a scalable architecture.}}
           \resumeItem{\normalsize{Worked closely with cross-functional teams to adopt best coding practices, ensuring clean, maintainable, and efficient code.}}
 
      \resumeItemListEnd  
  \resumeSubHeadingListEnd

    \resumeSubheading
      {Solulab, Ahamdabad \href{certificate Link}{\raisebox{-0.1\height}\faExternalLink }}{06 2024 --  09 2024}
      {\underline{Vocational Trainee (NodeJS) Intern}}{Remote}
      \vspace{-0pt}
      \resumeItemListStart
        \resumeItem{\normalsize{Contributed to designing and implementing \textbf{RESTful APIs} using \textbf{TypeScript} for various applications, ensuring robust functionality and secure data handling.}}
         \resumeItem{\normalsize{Worked with MongoDB database to manage data storage, retrieval, and integration within applications.}}
          \resumeItem{\normalsize{Worked with Microservices Architecture and learned \textbf{RabbitMQ} Message Broking Service to establish connection between two Microservices and \textbf{Docker} for containerization. }}
 
      \resumeItemListEnd  
  \resumeSubHeadingListEnd
  \vspace{1pt}

    \resumeSubheading
      {Celebal Technologies, Jaipur \href{https://drive.google.com/file/d/1jTqO9w0p2rVOXXlVBa6pi6FdzTVWM7FQ/view?usp=drive_link}{\raisebox{-0.1\height}\faExternalLink }}{05 2024 --  07 2024}
      {\underline{NodeJS Intern}}{Remote}
      \vspace{-2pt}
      \resumeItemListStart
        
          \resumeItem{\normalsize{Contributed to develop Node Applications 
ensuring robust functionality and secure data handling }}
 \resumeItem{\normalsize{Integrated Payment gateway system (Instamojo and Paypal)}}
 
      \resumeItemListEnd  
  \resumeSubHeadingListEnd
\vspace{-8pt}


%-----------PROGRAMMING SKILLS-----------
\section{TECHNICAL SKILLS}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{\normalsize{Languages:}}{ \normalsize{C, C++,  JavaScript}} \\
     \textbf{\normalsize{Developer Tools:}}{ \normalsize{VS Code, Jira(Atlasian), Firebase, Kubernetes, Jenkins}} \\
     \textbf{\normalsize{Technologies/Frameworks:}}{\normalsize{ GitHub(Version Control), ReactJS, React Native, Redux, NodeJS, ExpressJS, Git, MongoDB}} \\
    }}
 \end{itemize}
 \vspace{-15pt}





%-----------PROJECTS-----------
\section{PERSONAL PROJECTS}
    \vspace{-5pt}
    \resumeSubHeadingListStart
       \resumeProjectHeading
          {\href{https://invertisnews.000webhostapp.com/index.php}{\textbf{\large{\underline{InvertisCare: Complaint Platform}}} \href{Project Link}{\raisebox{-0.1\height}\faExternalLink }} $|$ \large{\underline{ReactJs, ExpressJs, NodeJS, MongoDB, mongoose}}}{02 2024}
            \vspace{-8pt}
          \resumeItemListStart
            \resumeItem {\normalsize {Complaint Submission: \textbf{500+} users registered at the portal. An easy-to-use form for students to submit complaints, including categories and detailed descriptions.
}}
            \resumeItem{\normalsize{Complaint Tracking: Students can view the status of their complaints and receive updates.}}
            \resumeItem{\normalsize{Admin Panel: A separate interface for university administrators that reduces the time to view, manage, and resolve complaints by  \textbf{30{\%}}.
            }}
            \resumeItem{\normalsize{Increased the efficiency of lodging and resolving student complaints by \textbf{45{\%}}.
            }}

            
            
          \resumeItemListEnd 
          \vspace{-13pt}
         
      \resumeProjectHeading
          {\href{https://github.com/guptatejasv/Featured-Chat-App.git}{\textbf{\large{\underline{VibeWire }}} \href{Project Link}{\raisebox{-0.1\height}\faExternalLink }} $|$ \large{\underline{Socket.io, JavaScript, NodeJS, Express, MongoDB(Database), eJS }}}{07 2024}
            \vspace{-8pt}
          \resumeItemListStart
            \resumeItem{\normalsize{\textbf{VibeWire} is a Real Time Chat Application created using socket.io. This chat application designed to facilitate seamless communication between users.}}
             \resumeItem{\normalsize{\textbf{Real-Time Messaging:} Supports 1-to-1 chat with instant message delivery.}}
             \resumeItem{\normalsize{\textbf{User Presence:} Real-time status updates (online/offline) for up to 1,000 users.}}
              \resumeItem{\normalsize{\textbf{Chat History:}Stores up to 10,000 messages per user for access and review.
                }}
           
          \resumeItemListEnd
          \vspace{20pt}

%






%------RELEVANT COURSEWORK-------
\section{COURSEWORK / SKILLS}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-2pt, parsep=5pt]
                \item Data Structures \& Algorithms
                \item Operating Systems
                \item Compiler Design
                \item  GKE, CloudSQL, VMs
               \item DevOps Tools: Git,
                        Docker
                      \item   CI/CD
                            pipelines
         
              
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd





 
 %-----------CERTIFICATIONS---------------
\section{CERTIFICATIONS}


$\sbullet[.75] \hspace{0cm}$ {\href{https://www.hackerrank.com/certificates/e0dc1f98230f}{JavaScript(Basics)- HackerRank}} \hspace{0.5cm}
$\sbullet[.5] \hspace{0.1cm}$ {\href{https://www.hackerrank.com/certificates/35ddd142df44}{CSS (Basics)- HackerRank}} \hspace{0.5cm}
$\sbullet[.5] \hspace{0.2cm}${\href{https://www.hackerrank.com/certificates/4392cbf0508a} {Problem Solving (Basics)- HackerRank}}\\


$\sbullet[.75] \hspace{0.2cm}${\href{https://www.hackerrank.com/certificates/90e93a3ef140}{Problem Solving (Intermediate)- HackerRank}} \hspace{1cm}
$\sbullet[.75] \hspace{0.1cm}$ {\href{https://www.hackerrank.com/certificates/0c8ab9e2960a}{SQL HackerRank Certification (Basics)}} \hspace{2.6cm}

$\sbullet[.75] \hspace{0.1cm}$ {\href{https://drive.google.com/file/d/1S1wRK5fm6CGY2MXcZqkmtFNMBcgmcdo4/view?usp=drive_link}{Python Essential Training(2022)}} \hspace{2.6cm}

$\sbullet[.75] \hspace{0.1cm}$ {\href{}{React Native: Practical Guide (Udemy)}} \hspace{2.6cm}
$\sbullet[.75] \hspace{0.1cm}$ {\href{}{NodeJs, ExpressJS and MongoDB (Udemy)}} \hspace{2.6cm}

%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Invertis University, Bareilly}{08 2022 -- Current}
      {B.Tech CSE - \textbf{Percentage} - \textbf{84.24}}{Bareilly, India}
  \resumeSubHeadingListEnd
 
  \resumeSubHeadingListStart
    \resumeSubheading
      {CSJM University, Kanpur}{08 2019 -- 08 2022}
      {B.Sc (PCM)\textbf \textbf{}}{Kanpur, India}
  \resumeSubHeadingListEnd

\end{document}




